Verifying Demonstrations

### 2017-08-24 SystemModel.tex
Adds question about Merkle tree
Replaces blockchain with t-poset

  \pause{}
  }
\begin{question}
  How should this one relate to the \acp{LP} and blockchain?
\end{question}
\end{frame}

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=right,level distance=5em}
    \Tree [.Proof
      [.{wsig} {\(x,y\)} [.{osig} [.{\(id\)} manifesto ] head ] [.tsig head'' ] ]
      {\dots}
      [.{wsig} {\dots} ]
    ]
  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the blockchain.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnesses by a trusted witness (tsig).
    }
  }
\end{figure}
\end{frame}

@@

>>>>

  \pause{}
  }
\begin{question}
  How should this one relate to the \acp{LP} and \ac{tposet}?
\end{question}
\end{frame}

\begin{frame}
\begin{figure}
  \centering
  \begin{tikzpicture}
    \tikzset{grow'=right,level distance=5em}
    \Tree [.Proof
      [.{wsig} {\(x,y\)} [.{osig} [.{\(id\)} manifesto ] head ] [.tsig head'' ] ]
      {\dots}
      [.{wsig} {\dots} ]
    ]
  \end{tikzpicture}
  \mode<article>{%
    \caption{%
      The proof depends on several witness signatures (wsig), each of which 
      depends on the owner's signature (osig), which depends on the \(id\) of the
      protest and the head of the \ac{tposet}.
      Whenever possible, the witness signature should include proof that the 
      witness themself has been witnessed by a trusted witness (tsig).
    }
  }
\end{figure}
\end{frame}

@@

More formally \dots
